### 2023-09-23 spanish/sections/papers.tex
Update papers.tex

\item{Olivares, A., González-Bustamante, B., Meneses, J., \& Rodríguez, M. (2014). Los think tanks en el gabinete: una exploración del caso chileno (2006-2014). {\itshape Revista de Sociología,} 29, 37--54. {\scshape doi}: \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.} \vspace{1mm} %% {\scshape url:} \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}

>>>>

\item{Olivares, A., González-Bustamante, B., Meneses, J., \& Rodríguez, M. (2014). Los think tanks en el gabinete: una exploración del caso chileno (2006-2014). {\itshape Revista de Sociología,} 29, 37--54. {\scshape url:} \\ \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{\textcolor{blue}{https://revistadesociologia.uchile.cl}}.} \vspace{1mm} %% {\scshape doi}: \\ \href{https://doi.org/10.5354/0719-529X.2014.36177}{\textcolor{blue}{10.5354/0719-529X.2014.36177}}.
